The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 author.tex
Add ORCID number
Comma and space before zip code

\author{T. Babej}
\affiliation{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}

@@

\author[0000-0002-8134-9591]{J. P. Dietrich}
\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany}
\affiliation{Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}

@@

\author[0000-0002-6324-5713]{M. Mastropietro}
\affiliation{Department Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}

@@

\author{M. N{\"o}the}
\affiliation{TU Dortmund, Experimental Physics 5, Otto-Hahn-Str. 4, 44221 Dortmund, Germany}

>>>>

\author[0000-0002-8222-3595]{T. Babej}
\affiliation{Department of Theoretical Physics \& Astrophysics, Masaryk University, Kotlarska 2, 61137 Brno, Czech Republic}

@@

\author[0000-0002-8134-9591]{J. P. Dietrich}
\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 1, 81679 Munich, Germany}
\affiliation{Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}

@@

\author[0000-0002-6324-5713]{M. Mastropietro}
\affiliation{Department of Physics and Astronomy, Ghent University, Krijgslaan 281, S9, B-9000 Gent, Belgium}

@@

\author{M. N{\"o}the}
\affiliation{Experimental Physics 5, TU Dortmund, Otto-Hahn-Str. 4, 44227 Dortmund, Germany}
